The population of long-period exoplanets --- \\ Fully-automated discovery \& characterization of long-period transiting exoplanet candidates in the \kepler\ archive

### 2016-04-19 document/ms.tex
nothing really

The model comparison step is computationally expensive because we estimate the
marginalized likelihoods for the light curve data under several different
models describing a transit and many other processes that ``look'' like
transits but are actually caused by noise.
This step is also conservative; unless a signal is a very convincing transit,
it won't pass the test.
In practice, this means that all but the highest signal-to-noise events will
be rejected at this step.
Therefore, in the inexpensive first step---the initial candidate search---we
can restrict the candidate list to high signal-to-noise events without a
substantial loss in detection efficiency.

>>>>

The model comparison step (step 2) is the key component of our method that
enables robust automation but it is also computationally expensive because we
must estimate the marginalized likelihoods for the light curve under several
different models describing a transit and many other processes that ``look''
like transits but are actually caused by noise.
This step is also conservative; unless a signal is a very convincing transit,
it won't pass the test.
In practice, this means that all but the highest signal-to-noise events will
be rejected at this step.
Therefore, in the inexpensive first step---the initial candidate search---we
can restrict the candidate list to high signal-to-noise events without a
substantial loss in detection efficiency.
